% Chapter 7
\chapter{The $L^p$ Spaces: Completeness and Approximation}

% 7.1
\section{Normed Linear Spaces}
\begin{flushleft}
	
	Throughout this chapter $E$ denotes a measurable set of real numbers.
	Define $\mathcal{F}$ to be the collection of all measurable extended real-valued functions on $E$ that are finite a.e. on $E$.
	We can say that two functions $f,g\in\mathcal{F}$ are equivalent, denoted by $f\cong g$, provided
	\[
	f(x)=g(x)\text{ for almost all }x\in E.	
	\]
	This is an equivalence relation and induces a partition of $\mathcal{F}$ into a disjoint collection of equivalence classes, denoted by $\mathcal{F}/\cong$, which is a linear space.
	There is a natural family $\{L^p(E)\}_{1\le p\le\infty}$ of subspaces of $\mathcal{F}/\cong$.
	\\
	For $1\le p<\infty$, define $L^p(E)$ to be the collection of equivalence class $[f]$ for which 
	\[
	\int_E|f|^p<\infty.	
	\]
	Then if $f\cong g$, then $\int_E|f|^p=\int_E|g|^p$.
	Showing that $L^p(E)$ is closed under linear combinations will prove that $L^p(E)$ is a linear subspace.
	To do this, let $c=\max\{|a|,|b|\}$ so that
	\[
	|a+b|\le|a|+|b|\le 2c,
	\]
	which implies
	\[
	|a+b|^p\le 2^pc^p\le2^p(|a|^p+|b|^p).	
	\]
	This inequality, together with the linearity and monotonicity of integration tells us that 
	\[
		\int_E|\alpha f+\beta g|^p \le 2^p(|\alpha|^p\int_E|f|^p+|\beta|^p\int_E| g|^p)<\infty.
	\]
	That is, for $[f],[g]\in L^p(E)$, then $\alpha[f]+\beta[g]\in L^p(E)$.\\
	We call a function $f\in\mathcal{F}$ \textbf{essentially bounded} provided there is some $M\ge 0$, called an \textbf{essential upper bound} for $f$, for which
	\[
	|f(x)|\le M\text{ for almost all }x\in E.	
	\]
	Then we can define $L^\infty(E)$ to be the collection of equivalence classes $[f]$ for which $f$ is essentially bounded. 
	Clearly $L^\infty(E)$ is a linear subspace because
	\[
	|\alpha f(x)+\beta g(x)|\le|\alpha| |f(x)|+|\beta|| g(x)|\le |\alpha| M + |\beta|M' = M'' \text{ a.e. on $E$}
	\]
	To state that a function $f$ in $L^p[a,b]$ is continuous means that there is a continuous function that agrees with $f$ a.e. on $[a,b]$.
	There is only one such continuous function and it is often convenient to consider this unique continuous function as the representative of $[f]$.\\
	It is useful to consider real-valued functions that have as their domain linear spaces of functions: such functions are called \textbf{functionals}.

	\begin{namedthm*}{Definition}
		Let $X$ be a linear space.
		A real-valued functional $\|\cdot\|$  on $X$ is called a \textbf{norm} provided for each $f$ and $g$ in $X$ and each real number $\alpha$,\\
		(The Triangle Inequality)
		\[
			\|f+g\|\le\|f\|+\|g\|,
		\]
		(Positive Homogeneity)
		\[
			\|\alpha f\|=|\alpha|\|f\|,	
		\]
		(Nonnegativity)
		\[
			\|f\|\ge 0\text{ and }\|f\|=0 \iff f=0.
		\]
	\end{namedthm*}
	A \textbf{normed linear space} is a linear space together with a norm.
	If $X$ is a linear space normed by $\|\cdot\|$ we say that a function $f$ in $X$ is a \textbf{unit function} provided $\|f\|=1$.
	For any $f\in X,f\neq 0$, the function $\frac{f}{\|f\|}$ is a unit function: it is a scalar multiple of $f$ which we call the \textbf{normalization} of $f$.

	\begin{namedthm*}{Example}[The Normed Linear Space $L^1(E)$]
		For a function $f$ in $L^1(E)$, define
		\[
		\|f\|_1=\int_E|f|.	
		\]
		Then $\|\cdot\|$ is a norm on $L^1(E)$.
	\end{namedthm*}

	\begin{namedthm*}{Example}[The Normed Linear Space $L^\infty(E)$]
		
	\end{namedthm*}

\end{flushleft}
\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
	\setcounter{enumi}{0}
	\item For $f$ in $C[a,b]$, Define
	\[
	\| f \|_1 = \int_a^b |f|.	
	\]
	Show that this is a norm on $C[a,b]$.
	Also show that there is no number $c \ge 0$ for which
	\[
	\| f \|_{\max}	\le c \| f \|_1 \text{ for all $f$ in $C[a,b]$},
	\]
	but there is a $c \ge 0$ for which 
	\[
	\| f \|_1	\le c \| f \|_{\max} \text{ for all $f$ in $C[a,b]$}.
	\]
	\item Let $X$ be the family of all polynomials with real coefficients defined on $\mathbb{R}$.
	Show that this is a linear space. For a polynomial $p$, define $\| p\|$ to be the sum of the absolute values of the coefficients of $p$.
	Is this a norm?
	\item For $f$ in $L^1[a,b]$, define $\|f\| = \smallint_a^b x^2 |f(x)|dx$.
	Show that this is a norm on $L^1[a,b]$.
	\item For $f$ in $L^\infty[a,b]$, show that 
	\[
	\| f\|_\infty = \min \biggl \{ M \ \biggl |\ m \{x \in [a,b]\ |\ |f(x)| > M \} =0 \biggr \},
	\] 
	and if, furthermore, $f$ is continuous on $[a,b]$, that
	\[
	\| f \|_{\infty} = \| f \|_{\max}.	
	\]
	\item Show that $\ell^\infty$ and $\ell^1$ are normed linear spaces.
\end{enumerate}

% 7.2
\section{The Inequalities of Young, H\"older, and Minkowski}

% 7.3
\section{$L^p$ is Complete: The Riesz-Fischer Theorem}

% 7.4
\section{Approximation and Separability}
