% Chapter 9
\authoredby{inprogress}
\chapter{Metric Spaces: General Properties}

% 9.1
\authoredby{inprogress}
\section{Examples of Metric Spaces}
\begin{flushleft}

"The object of the present chapter is to study general spaces called metric spaces for which the notion of distance between two points is fundamental."

\begin{namedthm*}{Definition}
    Let $X$ be a nonempty set. A function $\rho:X\times X\to\mathbb{R}$ is called a \textbf{metric} provided for all $x,y,z\in X$,
    \begin{enumerate}[label=(\roman*),align=right]
        \item $\rho(x,y)\ge0$,
        \item $\rho(x,y)=0$ iff $x=y$,
        \item $\rho(x,y)=\rho(y,x)$,
        \item $\rho(x,y)\le\rho(x,z)+\rho(z,y)$.
    \end{enumerate}
    A nonempty set together with a metric on the set is called a \textbf{metric space}, often denoted by $(X,\rho)$.
\end{namedthm*}

An example of a metric space is the set $\mathbb{R}$ of all real numbers with the metric $\rho(x,y) = |x-y|$. \par\medskip

A linear space with a norm is called a normed linear space.
A norm $\|\cdot\|$ on a linear space $X$ induces a metric $\rho$ on $X$ by defining
\[
    \rho(x,y)=\|x-y\|\text{ for all }x,y\in X.  
\]
To show this, let $x,y\in X$. Because $X$ is a linear space, $x-y \in X$, and $\|x-y\|$ is defined.
\begin{enumerate}[label=(\roman*),align=right]
    \item $\|x-y\|\ge0$ by positive definiteness of norm
    \item $\|x-y\|=0$ iff $x-y=0 \implies x=y$ by positive definiteness of norm
    \item $\|x-y\|=\|-1(y-x)\|=|-1|\|y-x\|=\|y-x\|$ by absolute homogeneity of norm
    \item $\|x-y\|= \|x-z+z-y\|\le\|x-z\|+\|z-y\|$ by subadditivity of norm
\end{enumerate}

Three prominent examples of normed linear spaces:
the Euclidean spaces $\mathbb{R}^n$, 
the $L^p(E)$ spaces,
$C[a,b]$.\\

For a natural number $n$, consider the linear space $\mathbb{R}^n$, whose points are $n$-tuples of real numbers.
For $x=(x_1,\cdots,c_n)\in\mathbb{R}^n$, the Euclidean norm $\|x\|$ is defined by
\[
    \|x\|=[x_1^2+\cdots+x_n^2]^{1/2}.    
\]
\par\medskip

\textit{The Discrete Metric}
For any nonempty set $X$, the discrete metric $\rho$ is defined by setting $\rho(x,y)=0$ if $x=y$ and $\rho(x,y)=1$ if $x\neq y$.
\begin{enumerate}[label=(\roman*),align=right]
    \item $\rho(x,y)\in\{0,1\}\implies\rho(x,y)\ge0$.
    \item $\rho(x,y)=0\iff x=y$ by definition.
    \item By symmetry of the equality relation,
    \[
    \rho(x,y)=
    \begin{cases}
        1 &x=y\\
        0 &x\neq y
    \end{cases}    
    =
    \begin{cases}
        1 &y=x\\
        0 &y\neq x
    \end{cases}  
    = \rho(y,x)
    \]
    \item In the case $x\neq y$, the triangle inequality is trivial.\\
    In the case $x=y$,\\
    if $x=z$, then by transitivity, $z=y$ and\\$\rho(x,y)=0,\rho(x,z)=0,\rho(z,y)=0$, and the triangle inequality is obvious: $0\le0$.\\
    if $x\neq z$, then by transitivity, $z\neq y$ and\\$\rho(x,y)=0,\rho(x,z)=1,\rho(z,y)=1 \implies \rho(x,y)=0\le2=\rho(x,z)+\rho(z,y)$.
\end{enumerate}
\par\medskip

\textit{Metric Subspaces}
For a metric space $(X,\rho)$, let $Y$ be a nonempty subset of $X$. 
Then the restriction of $\rho$ to $Y \times Y$ defines a metric on $Y$ and we call such a metric space a metric \textbf{subspace}.
Therefore every nonempty subset of Euclidean space, of and $L^p(E)$ space, $1\le p\le\infty$, and of $C[a,b]$ is a metric space.
\par\medskip

\textit{Metric Products}
For metric spaces $(X_1,\rho_1)$ and $(X_2,\rho_2)$, we define the \textbf{product metric} $\tau$ on the Cartesian product $X_1 \times X_2$ by setting, for $(x_1,x_2),(y_1,y_2)\in X_1 \times X_2$,
\[
    \tau((x_1,x_2),(y_1,y_2))= \{[\rho(x_1,y_1)]^2+[\rho(x_2,y_2)]^2\}^{1/2}.
\]
To see that this is a metric:
\begin{enumerate}[label=(\roman*),align=right]
    \item By metric property (i) of $\rho_1,\rho_2$, we have
    \begin{align*}
        \lbrack\rho_1(x_1,y_1)\rbrack^2\ge0\text{ and }\lbrack\rho_2(x_2,y_2)\rbrack^2\ge0
        &\iff \{\lbrack\rho_1(x_1,y_1)\rbrack^2+\lbrack\rho_2(x_2,y_2)\rbrack^2\}^{1/2}\ge0\\
        &\iff \tau((x_1,x_2),(y_1,y_2))\ge0
    \end{align*}
    \item By metric property (ii) of $\rho_1,\rho_2$, we have
    \begin{align*} 
        \tau((x_1,x_2),(y_1,y_2))&=\{\lbrack\rho_1 (x_1,y_1)\rbrack^2+\lbrack\rho_2 (x_2,y_2)\rbrack^2\}^{1/2}=0\\
        &\iff \lbrack\rho_1 (x_1,y_1)\rbrack^2=0\text{ and }\lbrack\rho_2 (x_2,y_2)\rbrack^2=0\\
        &\iff x_1=y_1\text{ and }x_2=y_2\\
        &\iff (x_1,x_2)=(y_1,y_2).
    \end{align*}
    \item By metric property (iii) (symmetry) of $\rho_1,\rho_2$, we have
    \begin{align*}
        \tau((x_1,x_2),(y_1,y_2)) &=\{\lbrack\rho_1 (x_1,y_1)\rbrack^2+\lbrack\rho_2 (x_2,y_2)\rbrack^2\}^{1/2}\\
        &=\{\lbrack\rho_1 (y_1,x_1)\rbrack^2+\lbrack\rho_2 (y_2,x_2)\rbrack^2\}^{1/2}\\
        &= \tau((y_1,y_2),(x_1,x_2)).
    \end{align*}
    \item We must first prove an inequality $\star$. Because $x^2\ge0$ for any real number $x$, we have
    \begin{align*}
        0&\le\lbrack\rho_1(x_1,z_1)\rho_2(z_2,y_2)-\rho_2(x_2,z_2)\rho_1(z_1,y_1)\rbrack^2\\
        0&\le\rho_1(x_1,z_1)^2\rho_2(z_2,y_2)^2+\rho_2(x_2,z_2)^2\rho_1(z_1,y_1)^2\\&\phantom{\le+{}}-2\rho_1(x_1,z_1)\rho_1(z_1,y_1)\rho_2(x_2,z_2)\rho_2(z_2,y_2)\\
        2\rho_1(x_1,z_1)\rho_1(z_1,y_1)\rho_2(x_2,z_2)\rho_2(z_2,y_2)&\le\rho_1(x_1,z_1)^2\rho_2(z_2,y_2)^2+\rho_2(x_2,z_2)^2\rho_1(z_1,y_1)^2\\
    \end{align*}
    Adding $\rho_1(x_1,z_1)^2\rho_1(z_1,y_1)^2 + \rho_2(x_2,z_2)^2\rho_2(z_2,y_2)^2$ to both sides, we have
    \begin{align*}
        \rho_1(x_1,z_1)^2\rho_1(z_1,y_1)^2 + \rho_2(x_2,z_2)^2\rho_2(z_2,y_2)^2+ 2\rho_1(x_1,z_1)\rho_1(z_1,y_1)\rho_2(x_2,z_2)\rho_2(z_2,y_2)\\
        \le\rho_1(x_1,z_1)^2\rho_1(z_1,y_1)^2 + \rho_2(x_2,z_2)^2\rho_2(z_2,y_2)^2+\rho_1(x_1,z_1)^2\rho_2(z_2,y_2)^2+\rho_2(x_2,z_2)^2\rho_1(z_1,y_1)^2\\
    \end{align*}
    Therefore we end up with the inequality: $\star$
    \begin{align*}
        \lbrack\rho_1(x_1,z_1)\rho_1(z_1,y_1) + \rho_2(x_2,z_2)\rho_2(z_2,y_2)\rbrack^2&\le\lbrack\rho_1(x_1,z_1)^2+\rho_2(x_2,z_2)^2\rbrack\lbrack\rho_1(z_1,y_1)^2+\rho_2(z_2,y_2)^2\rbrack\\
        \rho_1(x_1,z_1)\rho_1(z_1,y_1) + \rho_2(x_2,z_2)\rho_2(z_2,y_2)&\le\sqrt{\lbrack\rho_1(x_1,z_1)^2+\rho_2(x_2,z_2)^2\rbrack\lbrack\rho_1(z_1,y_1)^2+\rho_2(z_2,y_2)^2\rbrack}\\
        2\rho_1(x_1,z_1)\rho_1(z_1,y_1) + 2\rho_2(x_2,z_2)\rho_2(z_2,y_2)&\le2\sqrt{\rho_1(x_1,z_1)^2+\rho_2(x_2,z_2)^2}\sqrt{\rho_1(z_1,y_1)^2+\rho_2(z_2,y_2)^2}&&\star\\
    \end{align*}
    Now, to prove the triangle inequality of the product metric, we use the metric property (iv) (triangle inequality) of $\rho_1,\rho_2$:
    \begin{align*}
        &\rho(x_1,y_1)^2+\rho(x_2,y_2)^2\\
        &\le\lbrack\rho(x_1,z_1)+\rho(z_1,y_1)\rbrack^2+\lbrack\rho(x_2,z_2)+\rho(z_2,y_2)\rbrack^2\\
        &=\rho(x_1,z_1)^2+\rho(z_1,y_1)^2+2\rho(x_1,z_1)\rho(z_1,y_1)+\rho(x_2,z_2)^2+\rho(z_2,y_2)^2+2\rho(x_2,z_2)\rho(z_2,y_2)\\
        &\le\rho(x_1,z_1)^2+\rho(z_1,y_1)^2+\rho(x_2,z_2)^2+\rho(z_2,y_2)^2+2\sqrt{\rho_1(x_1,z_1)^2+\rho_2(x_2,z_2)^2}\sqrt{\rho_1(z_1,y_1)^2+\rho_2(z_2,y_2)^2}&&\star\\
        &=\biggl\lbrack\sqrt{\rho_1(x_1,z_1)^2+\rho_2(x_2,z_2)^2}+\sqrt{\rho_1(z_1,y_1)^2+\rho_2(z_2,y_2)^2}\biggr\rbrack^2
    \end{align*}
    Therefore we have
    \[
        \sqrt{\rho(x_1,y_1)^2+\rho(x_2,y_2)^2}\le\sqrt{\rho_1(x_1,z_1)^2+\rho_2(x_2,z_2)^2}+\sqrt{\rho_1(z_1,y_1)^2+\rho_2(z_2,y_2)^2}
    \]
    and thus
    \[
        \tau((x_1,x_2),(y_1,y_2)) \le \tau((x_1,x_2),(z_1,z_2))+\tau((z_1,z_2),(y_1,y_2)).
    \]
\end{enumerate}
This construction extends to countable products (problem 10).
\par\medskip

\begin{namedthm*}{Definition}
    Two metrics $\rho$ and $\sigma$ on a set $X$ are said to be \textbf{equivalent} provided there are positive numbers $c_1,c_2$ such that for all $x_1,x_2\in X$,
    \[
    c_1\cdot \sigma(x_1,x_2)\le\rho(x_1,x_2)\le c_2\cdot\sigma(x_1,x_2).    
    \]    
\end{namedthm*}

\begin{namedthm*}{Definition}
    A mapping $f$ from a metric space $(X,\rho)$ to a metric space $(Y,\sigma)$ is said to be an \textbf{isometry} provided it maps $X$ onto $Y$ and for all $x_1,x_2\in X$,
    \[
    \sigma(f(x_1),f(x_2))=\rho(x_1,x_2).    
    \]
\end{namedthm*}

Two metric spaces are called \textbf{isometric} provided there is an isometry from one onto the other.
To be isometric is an equivalence relation among metric spaces.
From the viewpoint of metric spaces, two isometric metric spaces are exactly the same, an isometry amounting merely to a relabeling of the points.
\par\medskip
In the definition of a metric $\rho$ on a set $X$ it is often convenient to relax the condition that $\rho(x,y)=0$ if and only if $x=y$.
When we allow the possibility that $\rho(x,y)=0$ for some $x\neq y$, we call $\rho$ a \textbf{pseudometric} and $(X,\rho)$ a pseudometric space.
On such a space, define the relation $x\cong y$ provided $\rho(x,y)=0$.
This is an equivalence relation that separates $X$ into a disjoint collection of equivalence classes $X/\cong$.  

\end{flushleft}
\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
	\setcounter{enumi}{0}
	\item Show that two metrics $\rho$ and $\tau$ on the same set $X$ are equivalent iff there is a $c>0$ such that for all $u,v\in X$,
	\[
        \frac{1}{c}\tau(u,v)\le\rho(u,v)\le c\tau(u,v).    
    \]
    Let $\rho$ and $\tau$ be two metrics on the same set $X$.\\
    $(\implies)$ Suppose $\rho$ and $\tau$ are equivalent.\\
    Then there exist $c_1,c_2>0$ such that for all $u,v\in X$,
    \[
    c_1\cdot \tau(u,v)\le\rho(u,v)\le c_2\cdot\tau(u,v).    
    \]
    By the Archimedean Property of $\mathbb{R}$, for the positive real number $c_1$, there exists a natural number $n$ for which $\frac{1}{n}<c_1$.\\
    Let $c=\max\{n,c_2\}$ so that $n\le c \implies \frac{1}{c}\le\frac{1}{n}<c_1$ and also $c_2\le c$, so we have
    \[
        \frac{1}{c}\cdot \tau(u,v)<c_1\cdot \tau(u,v)\le\rho(u,v)\le c_2\cdot\tau(u,v) \le c\tau(u,v).
    \]
    \\
    $(\impliedby)$ Suppose that there is a $c>0$ such that for all $u,v\in X$,
	\[
        \frac{1}{c}\tau(u,v)\le\rho(u,v)\le c\tau(u,v).    
    \]
    We showed that for a positive number $c$, its multiplicative inverse $\frac{1}{c}$ is also positive [ch1, 2(ii)], and so we have $\frac{1}{c},c>0$ such that for all $u,v\in X$,
    \[
        (\frac{1}{c})\tau(u,v)\le\rho(u,v)\le c\tau(u,v).    
    \]
    Therefore $\rho$ and $\tau$ are equivalent.
    \item Show that the following define equivalent metrics on $\mathbb{R}^n$:
    \begin{align*}
        \rho^*(x,y) &= |x_1-y_1| + \cdots + |x_n-y_n|;\\
        \rho^+(x,y) &= \max\{|x_1-y_1|, \cdots,|x_n-y_n|\}.
    \end{align*}
    For some $j\in\{1,\cdots,n\}$, we have $|x_j-y_j|=\max\{|x_1-y_1|, \cdots,|x_n-y_n|\}$.\\
    Then 
    \begin{align*}
        \rho^+(x,y) &= |x_j-y_j|\\
        &= 0+\cdots +|x_j-y_j|+\cdots+0\\
        &\le |x_1-y_1| + \cdots|x_j-y_j|+\cdots + |x_n-y_n|\\
        &= \rho^*(x,y).
    \end{align*}
    Also,
    \begin{align*}
        \rho^*(x,y) &= |x_1-y_1| + \cdots|x_j-y_j|+\cdots + |x_n-y_n|\\
        &\le |x_j-y_j| + \cdots|x_j-y_j|+\cdots + |x_j-y_j|\\
        &= n|x_j-y_j|\\
        &=n\rho^+(x,y).
    \end{align*}
    Therefore we have $1,n>0$ such that for all $x,y\in \mathbb{R}^n$,
    \[
        \rho^+(x,y)\le\rho^*(x,y)\le n\rho^+(x,y).
    \]
    Note that $\rho^*$ corresponds to what is called $\ell_1$ and $\rho^+$ corresponds to what is called $\ell_\infty$.
    In Chapter 13 Theorem 4 we discuss how any two norms on $R^n$ are equivalent.
    \item Find a metric on $\mathbb{R}^n$ that fails to be equivalent to either of those defined in the preceding problem.\\
    Let 
    \[
    \tau(x,y):=
    \begin{cases}
        \min\{|x-y|,1\}&\text{if both $x,y$ have each $x_i,y_i\in\mathbb{Q}$ or both $x,y$ have each $x_i,y_i\in\mathbb{Q}^c$,}\\
        1&\text{else}
    \end{cases}    
    \]
    Consider any $c_2>0$.
    Then choose a specific $\epsilon>0$ so that $\epsilon<\frac{1}{c_2}$.
    Then consider $x\in\mathbb{R}^n$ that has each $x_i\in\mathbb{Q}$.
    By the density of $\mathbb{Q}$ in $\mathbb{R}$ it is possible to find a sequence $\{x^k\}_k\subset \mathbb{R}^n$ that has each $x_i^k\in\mathbb{Q}$, and $x^k\to x$ (in $\rho=\rho^*$ or $\rho=\rho^+$).
    Choose $K$ large enough so that $\rho(x^K,x)<\epsilon$.
    However, then we have $\tau(x^k,x)=1>c_2\epsilon>c_2\rho(x^K,x)$, and thus $\tau(x^k,x)\not\le c_2\rho(x^K,x)$ and the metrics $\rho$ and $\tau$ are not equivalent.

    \item For a closed, bounded interval $[a,b]$, consider the set $X=C[a,b]$ of continuous real-valued functions on $[a,b]$.
    Show that the metric induced by the maximum norm and that induced by the $L^1[a,b]$ norm are not equivalent.\\
    From Chapter 7 Problem 1, we proved that there is no number $c \ge 0$ for which
	\[
	\| f \|_{\max}	\le c \| f \|_1 \text{ for all $f$ in $C[a,b]$}.
	\]
    Therefore there exists no $c_1,c_2>0$ such that for all $f,g$ in $C[a,b]$,
    \[
        c_1\| f-g \|_1 \le \| f-g \|_{\max}	\le c_2 \| f-g \|_1,
	\]
    and the metrics induced by the norms $\| \cdot \|_{\max}$ and $\| \cdot \|_1$ are not equivalent.
    \item \textit{The Nikodym Metric}. Let $E$ be a Lebesgue measurable set of real numbers of finite measure, $X$ the set of measurable subsets of $E$, and $m$ Lebesgue measure.
    For $A,B\in X$, define $\rho(A,B)=m(A\Delta B)$, where $A\Delta B = [A\setminus B]\cup[B\setminus A]$, the symmetric difference of $A$ and $B$.
    Show that this is a pseudometric on $X$.
    Define two measurable sets to be equivalent provided their symmetric difference has measure zero.
    Show that $\rho$ induces a metric on the collection of equivalence classes.
    Finally, show that for $A,B\in X$, 
    \[
    \rho(A,B)=\int_E|\chi_A-\chi_B|,    
    \]
    where $\chi_A$ and $\chi_B$ are the characteristic functions of $A$ and $B$, respectively.
    
    \begin{enumerate}[(i)]
        \item $\rho(A,B)=m(A\Delta B)\ge0$ by nonnegativity of Lebesgue measure.
        \item $A=B\implies \rho(A,B)=m[(A\setminus A)\cup(A\setminus A)]=0$.
        However, for sets $A\neq B$ but $A=B$ except for a set $C$ of $m$-measure zero (ex: $E=[0,2]$, $A=[0,1]$, $B=[0,1]\setminus\mathbb{Q}$), then $\rho(A,B)=m[(A\setminus B)\cup(B\setminus A)]=m[([0,1]\cap\mathbb{Q})\cup\emptyset]=0$.
        \item $\rho(A,B)=m[(A\setminus B)\cup(B\setminus A)]=m[(B\setminus A)\cup(A\setminus B)]=\rho(B,A)$.
        \item Through some movement we may obtain that 
        \begin{align*}
            [(A\setminus B)\cup(B\setminus A)]
            &=[(A\setminus B)\cup(B\setminus A)]\cap[C^c\cup C]\\
            &=([A\setminus C]\cap B^c)\cup([B\setminus C]\cap A^c)\cup([C\setminus B]\cap A)\cup([C\setminus A]\cap B)\\
            &\subset[(A\setminus C)\cup(C\setminus A)]\cup[(C\setminus B)\cup(B\setminus C)],
        \end{align*}
        and thus by monotonicity,
        \begin{align*}
            \rho(A,B)
            &\le m\left(\ [(A\setminus C)\cup(C\setminus A)]\cup[(C\setminus B)\cup(B\setminus C)]\ \right)\\
            &\le m[(A\setminus C)\cup(C\setminus A)]+m[(C\setminus B)\cup(B\setminus C)]\\
            &=\rho(A,C)+\rho(C,B).
            \end{align*}
    \end{enumerate}
    Thus $\rho$ is a pseudometric.
    \[
        \rho(A,B)=m[(A\setminus B)\cup(B\setminus A)]=\int_{E}1_{(A\setminus B)\cup(B\setminus A)}dm=\int_E|\chi_A-\chi_B|dm.
    \]
    \item Show that for $a,b,c\ge0$,
    \[
    \text{if }a\le b+c,\text{ then }\frac{a}{1+a}\le\frac{b}{1+b}+\frac{c}{1+c}.
    \]
    Because $a\le b+c$, we see that $\frac{1}{1+b+c}\le\frac{1}{1+a}$, and $-\frac{1}{1+a}\le-\frac{1}{1+b+c}$ so
    \begin{align*}
        \frac{a}{1+a}&=1-\frac{1}{1+a}\le1-\frac{1}{1+b+c}=\frac{b+c}{1+b+c}=\frac{b}{1+b+c}+\frac{c}{1+b+c}\le\frac{b}{1+b}+\frac{c}{1+c}.
    \end{align*}
    \item Let $E$ be a Lebesgue measurable set of real numbers that has finite measure and $X$ the set of Lebesgue measurable real-valued functions on $E$.
    For $f,g\in X$, define
    \[
    \rho(f,g)=\int_E\frac{|f-g|}{1+|f-g|}.    
    \]
    Use the preceding problem to show that this is a pseudometric on $X$. 
    Define two measurable functions to be equivalent provided they are equal a.e. on $E$.
    Show that $\rho$ induces a metric on the collection of equivalence classes.\\
    \\Let $f,g,h\in X$. 
    \\Then for all $x\in E$, we have the triangle inequality $|f(x)-g(x)|\le|f(x)-h(x)|+|h(x)-g(x)|$.
    By Problem 6 and monotonicity and linearity of integration, we have
    \[
        \int_E\frac{|f-g|}{1+|f-g|}\le\int_E\frac{|f-h|}{1+|f-h|}+\int_E\frac{|h-g|}{1+|h-g|},
    \]
    Therefore $\rho(f,g)\le\rho(f,h)+\rho(h,g)$ and (iv) holds.\\
    Clearly $\rho(f,g)\ge0$ is true so (i) holds.\\
    We also have $\rho(f,g)=\int_E\frac{|f-g|}{1+|f-g|}=\int_E\frac{|g-h|}{1+|g-h|}=\rho(g,f)$ so (iii) holds.\\
    However, (ii) does not hold. We can consider two functions $f,g\in X$ such that $f=g$ on $E\setminus E_0$, where $m(E_0)=0$.
    Then $ \rho(f,g)=\int_E\frac{|f-g|}{1+|f-g|}= \int_{E\setminus E_0}\frac{|f-f|}{1+|f-f|}=0$ but $f\neq g$.\\
    If we consider defining the equivalence 
    \[
        f\cong g\text{ when }f=g \text{ on }E\setminus E_0\text{ where }m(E_0)=0,
    \]
    Then $\rho$ now induces a metric on the collection of equivalence classes $X/\cong$, because we now have $ \rho(f,g)=0\iff f\cong g$.
    \item For $0<p<1$, show that 
    \[
    (a+b)^p\le a^p+b^p\text{ for all }a,b\ge0.    
    \]
    For any $b\ge0$, define $\varphi_b:[0,\infty)\to\mathbb{R}$ by $\varphi_b(a):=(a+b)^p-a^p-b^p$, so that $\varphi_b'(a)=p((a+b)^{p-1}-a^{p-1})$.
    Note that because $c:=p-1<0$, then $a\mapsto a^c$ is decreasing on $[0,\infty)$, and so $\varphi_b'(a)<0$ for each $a$.
    This implies that $(a+b)^p-a^p-b^p=\varphi_b(a)\le \varphi_b(0)=b^p-b^p=0$.

    \item For $E$ a Lebesgue measurable set of real numbers, $0<p<1$, and $g,h$ Lebesgue measurable functions on $E$ that have integrable $p^{th}$ powers, define
    \[
    \rho_p(h,g)=\int_E|g-h|^p.    
    \]  
    Use the preceding problem to show that this is a pseudometric on the collection of Lebesgue measurable functions on $E$ that have integrable $p^{th}$ powers.
    Define two such functions to be equivalent provided they are equal a.e. on $E$. 
    Show that $\rho_p(\cdot,\cdot)$ induces a metric on the collection of equivalence classes.
    \\Let $f,g,h:E\to\mathbb{R}$ such that $f,g,h$ are Lebesgue measurable and have integrable $p^{th}$ powers. 
    \\For all $x\in E$, Problem 8 tells us that $|g(x)-h(x)|^p\le|g(x)-f(x)|^p+|f(x)-h(x)|^p$.
    By monotonicity and linearity of integration, we have
    \[
        \int_E|g-h|^p\le\int_E|g-f|^p+\int_E|f-h|^p.
    \]
    Therefore $\rho_p(h,g)\le\rho_p(f,g)+\rho_p(h,f)$ and (iv) holds.\\
    Clearly $\rho_p(h,g)\ge0$ is true so (i) holds.\\
    We also have $\rho_p(h,g)=\int_E|g-h|^p=\int_E|h-g|^p=\rho_p(g,h)$ so (iii) holds.\\
    However, (ii) does not hold. We can consider two functions $h,g$ that are equivalent a.e. on $E$ but not equal.
    Then $ \rho_p(h,g)=\int_E|g-h|^p= \int_{E\setminus E_0}|g-h|^p=0$ with $m(E_0)=0$ but $h\neq g$.\\
    If we define an equivalence when two functions are equal a.e. on $E$, then $\rho_p$ is a metric on the collection of such equivalence classes. 
    \item Let $\{(X_n,\rho_n)\}_{n=1}^\infty$ be a countable collection of metric spaces.
    Use problem 6 to show that $\rho_*$ defines a metric on the Cartesian product $\prod_{n=1}^\infty X_n$, where for points $x = \{x_n\}$ and $y= \{y_n\}$ in $\prod_{n=1}^\infty X_n$,
    \[
    \rho_*(x,y)=\sum_{n=1}^\infty\frac{1}{2^n}\cdot\frac{\rho_n(x_n,y_n)}{1+\rho_n(x_n,y_n)}.    
    \]
    \item Let $(X,\rho)$ be a metric space and $A$ any set for which there is a one-to-one (injective) mapping $f$ of $A$ onto (surjective?) the set $X$ (bijection?).
    Show that there is a unique metric on $A$ for which $f$ is an isometry of metric spaces.
    (This is the sense in which an isometry amounts merely to a relabeling of the points in a space.)
    \item Show that the triangle inequality for Euclidean space $\mathbb{R}^n$ follows from the triangle inequality for $L^2[0,1]$.
    

\end{enumerate}

% 9.2
\authoredby{inprogress}
\section{Open Sets, Closed Sets, and Convergent Sequences}
\begin{namedthm*}{Definition}
    Let $(X,\rho)$ be a metric space. For a point $x\in X$ and $r>0$, the set 
    \[
        B(x,r)\equiv\{x'\in X:\rho(x',x)<r\}
    \]
    is called the \textbf{open ball} centered at $x$ of radius $r$.
    A subset $\mathcal{O}$ of $X$ is said to be \textbf{open} provided for every point $x\in\mathcal{O}$, there is an open ball centered at $x$ that is contained in $\mathcal{O}$.
    For a point $x\in X$, an open set that contains $x$ is called a \textbf{neighborhood} of $x$.
\end{namedthm*}

\begin{namedthm*}{Proposition 2}
    Let $X$ be a subspace of the metric space $Y$ and $E$ a subset of $X$.
    Then $E$ is open in $X$ iff $E=X\cap\mathcal{O}$, where $\mathcal{O}$ is open in $Y$.
\end{namedthm*}
\begin{proof}
    Suppose that $E$ is open in $X$.
    Then for every point $x\in E$, there is an open ball $B(x,r)=\{x'\in X:\rho(x,x')<r\}$.
    But $B(x,r)=X\cap\{x'\in Y:\rho(x,x')<r\}$, where $\{x'\in Y:\rho(x,x')<r\}$ is open in $Y$.

    Suppose that $E=X\cap\mathcal{O}$ for some $\mathcal{O}$ open in $Y$.
    Then for any $x\in E$, we have $x\in X$ and there exists $r>0$ such that $B(x,r)=\{x'\in Y:\rho(x,x')<r\}\subset\mathcal{O}$.
    But then 
    \[
        B'(x,r)=\{x'\in X:\rho(x,x')<r\}=X\cap B(x,r)\subset X\cap\mathcal{O}=E,
    \] 
    and thus $E$ is open in $X$.
\end{proof}
Example: for prop 2, consider the sets $Y=\mathbb{R}$, $X=[0,2]$ and $E=[0,1)$.
Then $E$ is not open in $Y$ but $E=[0,2]\cap(-1,1)$ is open in $X$.

\begin{namedthm*}{Definition}
    A sequence $\{x_n\}$ in a metric space $(X,\rho)$ is said to \textbf{converge} to the point $x\in X$ provided
    \[
        \lim_{n\to\infty}\rho(x_n,x)=0,
    \]
    that is, for each $\epsilon>0$, there is an index $N$ such that for every $n\ge N$, then $\rho(x_n,x)<\epsilon$.
    The point to which the sequence converges is called the \textbf{limit} of the sequence and we often write $\{X_n\}\to x$ to denote the convergence of $\{x_n\}$ to $x$.
\end{namedthm*}

\begin{namedthm*}{Proposition 7}
    Let $\rho$ and $\sigma$ be equivalent metrics on a nonempty set $X$.
    Then a subset of $X$ is open in the metric space $(X,\rho)$ iff it is open in the metric space $(X,\sigma)$.
\end{namedthm*}
\begin{proof}
    Suppose $E\subset X$ is open in $(X,\rho)$.
    Then for any $x\in E$, there exists $r>0$ such that $B_\rho(x,r)\subset E$; that is,
    \[
        \rho(x,e)<r\implies e\in E,
    \]
    and by the equivalence of metrics, there exists $c_1>0$ with
    \[
        c_1\cdot\sigma(x,e)<\rho(x,e)<r,
    \]
    which implies
    \[
        \sigma(x,e)<\frac{r}{c_1}\implies e\in E,
    \]
    and $B_\sigma(x,r/c_1)\subset E$.
\end{proof}

\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
    \setcounter{enumi}{12}
    \item In a metric space $X$, is it possible for $r>0$ and two distinct points $u$ and $v$ in $X$ to have $B(u,r)=B(v,r)?$
    Is this possible in Euclidean space $\mathbb{R}^n$?
    Is is possible in a normed linear space?

    Let $f:[0,1]\to\mathbb{R}$ be defined as $f(x)=1$ for $x$ rational, and $f(x)=0$ otherwise.
    Then $f=0$ $m$-a.e. (for $m$ Lebesgue measure).
    Consider the metric space ($X:=L^\infty([0,1]),\rho(f,g):=\|f-g\|_\infty$).
    Considering any $r>0$ and $B(f,r)=\{g\in X:\rho(f,g)<r\}$, note that because $f$ is zero except for a set of measure zero, then $r>\rho(f,g)=\|f-g\|_\infty=\text{esssup}_{[0,1]}|f-g|=\text{esssup}_{[0,1]}|g|=\|g\|_\infty=\rho(0,g)$.
    \item Let $(X,\rho)$ be a metric space in which $\{u_n\}\to u$ and $\{v_n\}\to v$.
    Show that $\{\rho(u_n,v_n)\}\to\rho(u,v)$.

    For any $\epsilon>0$, choose $n$ large enough so that both $\rho(u_n,u)<\epsilon/2$ and $\rho(v,v_n)<\epsilon/2$.
    Then by the triangle inequality applied twice, 
    \begin{align*}
        \rho(u_n,v_n)\le\rho(u_n,u)+\rho(u,v)+\rho(v,v_n)<\epsilon/2+\rho(u,v)+\epsilon/2,
    \end{align*}
    % Therefore 
    % \begin{align*}
    %     \rho(u_n,v_n)-\rho(u,v)\le\rho(u_n,u)+\rho(v,v_n)<\epsilon/2+\epsilon/2
    % \end{align*}
    and we are done as $\rho(u_n,v_n)-\rho(u,v)<\epsilon.$
    \item Let $X$ be a metric space, $x$ belong to $X$, and $r>0$.
    \begin{enumerate}[(i)]
        \item Show that $\overline{B}(x,r)$ is closed and contains $B(x,r)$.
        
        It is sufficient to show that the complement of $\overline B(x,r)$ in $X$ is open, and that $x\in B(x,r)\implies x\in\overline{B}(x,r)$.
        
        Let $y\in \overline{B}(x,r)^c$, so that $\rho(x,y)>r$.
        Then the ball $B(y,\rho(x,y)-r)\subset \overline{B}(x,r)^c$ because for $y'\in B(y,\rho(x,y)-r)$, then 
        \[ 
            \rho(x,y')\ge\rho(x,y)-\rho(y',y)>\rho(x,y)-(\rho(x,y)-r)=r,
        \]
        and $y'\in\overline{B}(x,r)$.
        
        Let $z\in B(x,r)$. 
        Then clearly $\rho(x,z)<r\le r$ implies that $z\in\overline{B}(x,r):\{x'\in X:\rho(x,x')\le r\}$.
        \item Show that in a normed linear space $X$ the closed ball $\overline{B}(x,r)$ is the closure of the open ball $B(x,r)$, but this isn't so in a general metric space.
        TBD
    \end{enumerate}
    \item Prove Proposition 2.

    Proved above.
    \item Prove Proposition 7.
    
    Proved above.
    \item Let $X$ be a subspace of the metric space $Y$ and $A$ a subset of $X$.
    Show that $A$ is closed in $X$ if and only if $A=X\cap F$, where $F$ is closed in $Y$.
    
    
    \item Let $X$ be a subspace of the metric space $Y$.
    \begin{enumerate}
        \item If $\mathcal{O}$ is an open subset of the metric subspace $X$, is $\mathcal{O}$ an open subset of $Y$?
        What if $X$ is an open subset of $Y$?
        \item If $F$ is a closed subset of the metric subspace $X$, is $F$ a closed subset of $Y$?
        What if $X$ is a closed subset of $Y$?
    \end{enumerate}
    \item For a subset $E$ of a metric space $X$, a point $x\in X$ is called an interior point of $E$ provided there is an open ball centered at $x$ that is contained in $E$:
    the collection of interior points of $E$ is called the interior of $E$ and denoted by int $E$.
    Show that int $E$ is always open and $E$ is open iff $E=$ int $E$.
    \item For a subset $E$ of a metric space $X$, a point $x\in X$ is called an exterior point of $E$ provided there is an open ball centered at $x$ that is contained in $X\setminus E$: 
    the collection of exterior points of $E$ is called the exterior of $E$ and denoted by ext $E$.
    Show that ext $E$ is always open.
    Show that $E$ is closed iff $X\setminus E=$ ext $E$.
    \item For a subset $E$ of a metric space $X$, a point $x\in X$ is called a boundary point of $E$ provided every open ball centered at $x$ contains points in $E$ and points in $X\setminus E$:
    the collection of boundary points of $E$ is called the boundary of $E$ and denoted by bd $E$.
    Show 
    \begin{enumerate}[(i)]
        \item that bd $E$ is always closed,
        \item that $E$ is open iff $E\cap$ bd $E=\emptyset$,
        \item that $E$ is closed iff bd $E\subset E$.
    \end{enumerate}
    \item Let $A$ and $B$ be subsets of a metric space $X$.
    Show that if $A\subseteq B$, then $\overline{A}\subset\overline{B}$.
    Also, show that $(\overline{A\cup B})=\overline{A}\cup\overline{B}$ and $(\overline{A\cup B})\subseteq\overline{A}\cap\overline{B}$.
    \item Show that for a subset $E$ of a metric space $X$, the closure of $E$ is the intersection of all closed subsets of $X$ that contain $E$.
\end{enumerate}

% 9.3
\authoredby{inprogress}
\section{Continuous Mappings Between Metric Spaces}

\begin{namedthm*}{Definition}
    A mapping $f$ from a metric space $X$ to a metric space $Y$ is said to be continuous at the point $x\in X$ provided for any sequence $\{x_n\}$ in $X$,
    \[
        \text{if $\{x_n\}\to x$, then $\{f(x_n)\}\to f(x)$}.
    \]
    The mapping is said to be \textbf{continuous} provided it is continuous at every point in $X$.
\end{namedthm*}

\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
    \setcounter{enumi}{24}
    \item Exhibit a continuous mapping that is not uniformly continuous and a uniformly continuous mapping that is not Lipschitz.
    \item Show that every mapping from a metric space $(X,\rho)$ to a metric space $(Y,\sigma)$ is continuous if $\rho$ is the discrete metric.
    \item 
\end{enumerate}


% 9.4
\authoredby{untouched}
\section{Complete Metric Spaces}

\begin{namedthm*}{Definition}
    A sequence $\{x_n\}$ in a metric space $(X,\rho)$ is said to be a \textbf{Cauchy sequence} provided for each $\epsilon>0$, there is an index $N$ for which 
    \[
        \text{if }n,m\ge N,\text{ then }\rho(x_n,x_m)<\epsilon.
    \]
\end{namedthm*}
\begin{namedthm*}{Definiton}
    A metric space $X$ is said to be \textbf{complete} provided every Cauchy sequence in $X$ converges to a point in $X$.
\end{namedthm*}

\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
    \setcounter{enumi}{36}
    \item In a metric space $X$, show (i) that a convergent sequence is Cauchy and (ii) that a Cauchy sequence is bounded.
    
    See simply that, for any $\epsilon>0$, because the sequence is convergent, there exists the index $N$ so that $\rho(x_n,x)<\epsilon/2$ for any $n\ge N$.
    Therefore for any $n,m\ge N$, we have
    \[
        \rho(x_n,x_m)\le \rho(x_n,x)+\rho(x,x_m)<\epsilon/2+\epsilon/2,
    \]
    and the sequence is Cauchy.
    To show that any Cauchy sequence is bounded, consider $\epsilon=1$.
    Therefore there exists the index $N$ such that $n,m\ge N$ implies $\rho(x_n,x_m)<1$.
    Then in particular we have that 
    \[
        \text{diam}(\{x_n\}_n)\le \max\{\rho(x_1,x_2),\rho(x_1,x_3),\cdots,\rho(x_1,x_{N-1}),\rho(x_2,x_3),\cdots,\rho(x_{N-2},x_{N-1}),1\},
    \]
    and the sequence is bounded.
\end{enumerate}

% 9.5
\authoredby{untouched}
\section{Compact Metric Spaces}

\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
    \setcounter{enumi}{50}
    \item 
\end{enumerate}

% 9.6
\authoredby{untouched}
\section{Separable Metric Spaces}
\begin{center}
	\textbf{PROBLEMS}
\end{center}
\begin{enumerate}
    \setcounter{enumi}{73}
    \item 
\end{enumerate}
